% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% cv.tex                                 %%
%% <https://github.com/aliyazdi75/Resume> %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,MMMyyyy,nonstopmode]{resume}

\usepackage{xcolor}
\usepackage{multicol}
\usepackage{slantsc}
\usepackage{ragged2e}
\usepackage{enumitem}
\usepackage{fontawesome5}

%% Use ctrl+alt+j (cmd+option+j on Mac) to refrence on pdf %%
%%%%%%%%%%%%%%
%% PREAMBLE %%
%%%%%%%%%%%%%%

% Multi Cols no justify.
\AtBeginEnvironment{multicols}{\RaggedRight}

% CV Info.
\newcommand{\CVAuthor}{Ali Yazdi}
\newcommand{\CVTitle}{Ali Yazdi's Resume}
\newcommand{\TitleDesciption}{Senior Flutter Developer, Community Organizer}
\newcommand{\CVNote}{Last Update on \today}
\newcommand{\CVWebpageName}{yazdi.ca}
\newcommand{\CVWebpage}{https://yazdi.ca}
\newcommand{\MainEmailName}{ma.yazdi75@gmail.com}
\newcommand{\MainEmail}{mailto:ma.yazdi75@gmail.com}
\newcommand{\SecondoryEmailName}{a.yazdi@gdgmontreal.com}
\newcommand{\SecondoryEmail}{mailto:a.yazdi@gdgmontreal.com}
\newcommand{\PhoneName}{(438)\,929-3675}
\newcommand{\Phone}{tel:+14389293675}
\newcommand{\Address}{Montréal, Québec, Canada}
\newcommand{\PDFKeywords}{resume, cv, aliyazdi75, \CVAuthor, flutter, developer}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={aliyazdi75},
pdfproducer={aliyazdi75},
pdfkeywords={\PDFKeywords},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks,
colorlinks, 
urlcolor=teal,
linkcolor=teal
}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

\newcommand\pscircled[1]{%
\raisebox{-0.315\height}{\begin{postscript}
\Cnodeput[radius=2.3ex](0,0){P}{#1}
\end{postscript}}}

%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT %%
%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%
%% TITLE BLOCK %%
%%%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
    \normalsize{
        \href{https://linkedin.com/in/aliyazdi75}
        {\faLinkedin}
        \,\textbullet\,
        \href{https://github.com/aliyazdi75}
        {\faGithub}
        \,\textbullet\,
        \href{https://aliyazdi75.medium.com}
        {\faMedium}
        \,\textbullet\,
        \href{mailto:ma.yazdi75@gmail.com}
        {\faEnvelope}
        \,\textbullet\,
        \href{\Phone}
        {\faPhone}
        \,\textbullet\,
        \href{\CVWebpage}
        {\faGlobe}
    }
    \par
    {\TitleDesciption}
    \par
    \href{\MainEmail}
    {\MainEmailName}
    \,\SubBulletSymbol\,
    \href{\SecondoryEmail}
    {\SecondoryEmailName}
    \,\SubBulletSymbol\,
    \href{\Phone}
    {\PhoneName}
    \,\SubBulletSymbol\,
    \href{\CVWebpage}
    {\CVWebpageName}
\end{SubTitle}

\smallskip\hrule

\begin{Body}

    %%%%%%%%%%%%%%
    %% ABOUT ME %%
    %%%%%%%%%%%%%%


    \Section
    {About Me}
    {About Me}
    {PDF:AboutMe}
    Experienced Flutter developer with a proven track record of delivering robust and scalable mobile applications. Committed to developing efficient and user-friendly solutions that consistently meet the highest quality standards. Passionate about continuous learning and staying updated with the latest industry trends, I actively leverage artificial intelligence and apply software engineering best practices to drive innovation and deliver exceptional results.

    %%%%%%%%%%%%%%%%%%%%%
    %% WORK EXPERIENCE %%
    %%%%%%%%%%%%%%%%%%%%%

    \Section
    {Work\newline
        Experience}
    {Work Experience}
    {PDF:WorkExperience}

    \Entry
    \href{https://woopen.com}
    {\textbf{Woopen}},
    {\small{Montréal, Canada\,\SubBulletSymbol\,Full-time}}
    \hfill
    \textsl{\small{\DatestampYM{2021}{08}\,--\,Present}}
    \Gap
    Senior Flutter Developer
    \normalsize{
        \SubBulletSymbol\,
        \href{https://play.google.com/store/apps/details?id=com.woopen.app}
        {\faGooglePlay}
        \SubBulletSymbol\,
        \href{https://apps.apple.com/app/woopen-immobilier-habitat/id1543053660}
        {\faAppStoreIos}}
    \BulletItem
    Woopen is a market network for all professionals, clients, stakeholders, and enthusiasts in the world of real estate and housing.
    \begin{Detail}
        \SubBulletItem
        Played a key role in the mobile project, taking ownership of the Flutter development and driving its success.
        \SubBulletItem
        Upgraded the application's Flutter version, implemented new features like null-safety and new localization, and refactored to a standard project code style with the help of analysis options.
        \SubBulletItem
        Improved the application's structure, tests, and stability based on fixing Sentry issues, migrating to null-safety, reducing asset files, using icon fonts, and setting up the application for deferred components. Successfully reduced bugs by 70\% through the implementation of structured testing and bug fixing strategies, improved application performance by dropping useless frame rendering, achieved 20ms less rendering time in profile mode, and drastically decreased application size by 89MB.
        \SubBulletItem
        Implemented automation between development tools, including Github actions, Sentry, Jira, Slack, and Lokalise, to streamline workflows and enhance collaboration.
        \SubBulletItem
        Collaborated with an external software organization in an agile team, working on the development of new features as requested by the business side.
    \end{Detail}

    \BigGap
    \Entry
    \href{https://en.iranian.ac.ir/}
    {\textbf{Iranian University}},
    {\small{Tehran, Iran\,\SubBulletSymbol\,Full-time}}
    \hfill
    \textsl{\small{\DatestampYM{2020}{04}\,--\,\DatestampYM{2021}{08}}}
    \Gap
    Software Engineer
    \BulletItem
    The Iranian University is the first e-institute of higher education in Iran.
    \begin{Detail}
        \SubBulletItem
        Implemented agile methodologies to optimize student registration and exam season productivity, resulting in improved efficiency.
        \SubBulletItem
        Developed robust APIs for the E-Learning Management System (\href{https://ems.iranian.ac.ir/?lang=en}{EMS}), facilitating seamless management of student and professor data for unit registration, grades, and payments.
        \SubBulletItem
        Optimized database performance and implemented caching strategies to significantly enhance the server response time of the EMS platform.
    \end{Detail}

    \BigGap
    \Entry
    \href{https://matemachine.com}
    {\textbf{Mate Machine}},
    {\small{Remote\,\SubBulletSymbol\,Part-time project}}
    \hfill
    \textsl{\small{\DatestampYM{2020}{07}\,--\,\DatestampYM{2021}{06}}}
    \Gap
    Freelance Flutter Developer
    \BulletItem
    Mate Machine is a dating social media startup company.
    \begin{Detail}
        \SubBulletItem
        Transformed the app architecture to leverage Flutter's best practices, ensuring scalability and maintainability.
        \SubBulletItem
        Implemented a robust SignalR socket client to facilitate real-time social media chat, enhancing user engagement.
        \SubBulletItem
        Leveraged Firebase services, including Cloud Messaging, Analytics, and Crashlytics, to enhance app functionality and monitor performance.
        \SubBulletItem
        Developed and integrated a seamless peer-to-peer (P2P) WebRTC video chatting feature, enabling users to connect effortlessly.
    \end{Detail}

    \BigGap
    \Entry
    \href{https://tarafdari.com}
    {\textbf{Tarafdari}},
    {\small{Tehran, Iran\,\SubBulletSymbol\,Full-time}}
    \hfill
    \textsl{\small{\DatestampYM{2019}{01}\,--\,\DatestampYM{2020}{04}}}
    \Gap
    Mobile Application Developer
    \normalsize{
        \SubBulletSymbol\,
        \href{https://play.google.com/store/apps/details?id=com.tarafdari.news}
        {\faGooglePlay}}
    \BulletItem
    Tarafdari is the first and most popular sports social media network with millions of users in Iran, providing official news and live scores
    of national and international matches.
    \begin{Detail}
        \SubBulletItem
        Developed and maintained mobile applications for a popular sports media platform using Flutter framework.
        \SubBulletItem
        Implemented key features such as live score updates, news feeds, and user profile management.
        \SubBulletItem
        Collaborated with a cross-functional team to ensure seamless integration with backend services and APIs.
        \SubBulletItem
        Developed and maintained a custom notification package, enhancing the user experience and increasing engagement.
        \SubBulletItem
        Designed and implemented a TV sport streaming feature with live chat functionality using SocketIO, allowing users to interact in real-time while watching sports events.
        \SubBulletItem
        Conducted thorough testing and debugging to deliver high-quality, bug-free applications by using Firebase crashlytics.
        \SubBulletItem
        Contributed to achieving thousands of downloads for the mobile application through effective development and optimization strategies.
    \end{Detail}

    %%%%%%%%%%%%%%%%%%
    %% PAGE BREAK   %%
    %%%%%%%%%%%%%%%%%%

    \newpage

    %%%%%%%%%%%%%%%
    %% EDUCATION %%
    %%%%%%%%%%%%%%%

    \Section
    {Education}
    {Education}
    {PDF:Education}

    \Entry
    \href{https://aut.ac.ir/en}
    {\textbf{Amirkabir University of Technology}},
    {\small{(Tehran Polytechnic), Tehran, Iran}}
    \hfill
    \textsl{\small{\DatestampYM{2015}{09}\,--\,\DatestampYM{2020}{09}}}

    \Gap
    \BulletItem
    Bachelor of Engineering (BSc.) in
    \href{https://ce.aut.ac.ir/en}
    {Computer Engineering, Software},
    \href{https://ur.isc.ac/#Technology?input_culture=en}
    {Ranked 1st}
    in Iran.
    \begin{Detail}
        \SubBulletItem
        Thesis:
        Designing and Implementing a Location-Based Social Network
        Recommendation System
        \SubBulletItem
        Adviser: Prof.~Mohammad~Rahmati,
        Record\,No.: 44430,
        Thesis\,No.: B9\,1668,
        Year: 2020
    \end{Detail}

    \BigGap
    \Entry
    \href{http://adab.sch.ir/HSchool}
    {\textbf{Adab High School}},
    {\small{Tehran, Iran}}
    \hfill
    \textsl{\small{\DatestampYM{2011}{09}\,--\,\DatestampYM{2014}{06}}}
    \Gap
    \BulletItem
    Diploma in Mathematics and Physics, {\small{\textsl{GPA: 19.31 / 20.00}}}

    %%%%%%%%%%%%%%%%%%%%%%
    %% TECHNICAL SKILLS %%
    %%%%%%%%%%%%%%%%%%%%%%

    \Section
    {Technical Skills}
    {Technical Skills}
    {PDF:TechnicalSkills}

    % \begin{multicols}{2}
    % \begin{itemize}[leftmargin=*]
    \BulletItem
    Programming Languages
    \begin{Detail}
        \Item
        Dart, Python, Java, C/C++, PHP, Assembly
    \end{Detail}

    \Gap
    \BulletItem
    Mobile \& Web Development
    \begin{Detail}
        \Item
        Flutter, Django, Django Rest Framework, Android
    \end{Detail}

    % \columnbreak

    \Gap
    \BulletItem
    Database \& Operating Systems
    \begin{Detail}
        \Item
        Linux (Ubuntu), PostgreSQL, MySQL
    \end{Detail}

    \Gap
    \BulletItem
    Tools \& Technologies
    \begin{Detail}
        \Item
        CI/CD, Docker, Git, \LaTeX, WebRTC, Scikit-learn, Pandas, Bash Scripting
    \end{Detail}

    \Gap
    \BulletItem
    Other
    \begin{Detail}
        \Item
        Software Systems Engineering, Cross-Platform Application Development
    \end{Detail}

    % \end{itemize}
    % \end{multicols}

    %%%%%%%%%%%%%%%%%%%%%%%%%
    %% VOLUNTEER EXPERIENCE %%
    %%%%%%%%%%%%%%%%%%%%%%%%%

    \Section
    {Volunteer Experience}
    {Volunteer Experience}
    {PDF:Volunteer Experience}

    \BulletItem
    \href{https://gdg.community.dev/gdg-montreal}
    {\textbf{Google Developer Group Montreal}},
    {\small{Montreal, Canada}}
    \hfill
    \textsl{\small\DatestampYM{2023}{03}\,--\,Present}
    \Item
    As an organizer and speaker for in-person Flutter events in Montreal, I collaborate with a team to plan and execute meetups, workshops, and conferences. I deliver presentations on Flutter-related topics, share my expertise, and engage with the community to foster knowledge exchange and networking opportunities.

    \BigGap
    \BulletItem
    \href{https://persianflutter.com}
    {\textbf{Persian Flutter Community}},
    {\small{Tehran, Iran}}
    \hfill
    \textsl{\small\DatestampYM{2021}{04}\,--\,Present}
    \Item
    As a community organizer and speaker for the Persian Flutter Community, I play an active role in coordinating virtual events, webinars, and online discussions. I contribute to the growth of the community by sharing insights, providing guidance to members, and delivering presentations on Flutter development best practices and emerging trends.

    %%%%%%%%%%%%%%%%%%%%%
    %% Honors & Awards %%
    %%%%%%%%%%%%%%%%%%%%%

    \Section
    {Honors \&\newline
        Awards}
    {Honors \& Awards}
    {PDF:HonorsAndAwards}

    \BulletItem
    Most installed sport application in Iran for Tarafdari application
    \hfill
    \textsl{\small{\DatestampYM{2020}{05}}}
    \begin{Detail}
        \Item
        Achieved more than 200k active users on the Google Play Store for Tarafdari application after migrating to Flutter.
    \end{Detail}

    \Gap
    \BulletItem
    First Place in the 12th Iran Web and Mobile Festival
    (\href{https://iwmf.ir}
    {\small{IWMF}})
    \hfill
    \textsl{\small{\DatestampYM{2020}{02}}}
    \begin{Detail}
        \Item
        Awarded for creating the Best Sport Mobile Application among 7k applications.
    \end{Detail}

    \Gap
    \BulletItem
    Ranked in top 0.2\% among more than 180K participants
    \hfill
    \textsl{\small{\DatestampYM{2015}{07}}}
    \begin{Detail}
        \Item
        Achieved a high ranking in the Nation-Wide University Entrance Exam among all National Students of Physics and Mathematics.
    \end{Detail}

    \Gap
    \BulletItem
    Qualified for the Second Round of Olympiad
    among more than 70K participants
    \hfill
    \textsl{\small{\DatestampYM{2013}{07}}}
    \begin{Detail}
        \Item
        Successfully qualified for the Iranian Physics and Mathematical Olympiad.
    \end{Detail}

    %%%%%%%%%%%%%%%%%%
    %% PUBLICATIONS %%
    %%%%%%%%%%%%%%%%%%

    \Section
    {Publications}
    {Publications}
    {PDF:Publications}

    \SubSection
    {Medium}
    {Medium}
    {PDF:Medium}

    % Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
    \begingroup
    \renewcommand{\MaxNumberedItem}{[88]}

    \BigGap
    \NumberedItem{[1]}
    \href{https://aliyazdi75.medium.com}
    {\underline{A. Yazdi}},
    \href{https://medium.com/flutter-community/lets-make-the-flutter-navigator-2-bc5953251c3e?source=friends_link&sk=e1ff30235ab93276b558c5b5ef1dd15f}
    {
        ``Let’s make the Flutter Navigator 2''
    },
    \newline Designing and Implementing Navigator 2 for the web applications support Imperative and Declarative Navigation,
    \href{https://medium.com/flutter-community}
    {\textit{Flutter Community}},
    \DatestampYM{2021}{04}

    \BigGap
    \NumberedItem{[2]}
    \href{https://aliyazdi75.medium.com}
    {\underline{A. Yazdi}},
    \href{https://medium.com/flutter-community/the-software-engineering-approach-in-cross-platform-programming-with-flutter-part-1-efcdc8a8fc26?source=friends_link&sk=ceb60f56685ce66c7f9574595748f25b}
    {
        ``Using Software Engineering methods to design and build a fully responsive and adaptive mobile, desktop, and web application''
    },
    \newline The first part of the Software Engineering approach in Cross-Platform Programming with Flutter,
    \href{https://medium.com/flutter-community}
    {\textit{Flutter Community}},
    \DatestampYM{2021}{03}

    \BigGap
    \NumberedItem{[3]}
    \href{https://aliyazdi75.medium.com}
    {\underline{A. Yazdi}},
    \href{https://medium.com/flutter-community/the-software-engineering-approach-in-cross-platform-programming-with-flutter-part-2-f7b75056102?source=friends_link&sk=79ed6a47bd6fe9b4247f3cc2a113e3df}
    {
        ``Designing and building the Flutter application structure using the Bloc pattern in the micro-service architecture''
    },
    \newline The second part of the Software Engineering approach in Cross-Platform Programming with Flutter,
    \href{https://medium.com/flutter-community}
    {\textit{Flutter Community}},
    \DatestampYM{2021}{02}

    \BigGap
    \NumberedItem{[4]}
    \href{https://aliyazdi75.medium.com}
    {\underline{A. Yazdi}},
    \href{https://medium.com/flutter-community/the-software-engineering-approach-in-cross-platform-programming-with-flutter-part-3-34c6eff02af0?source=friends_link&sk=a34a4a71f306e81b868fd6865abb6aaa}
    {
        ``Designing and developing the Flutter application data models and backend using the Build value and Bloc pattern''
    },
    \newline The third part of the Software Engineering approach in Cross-Platform Programming with Flutter,
    \href{https://medium.com/flutter-community}
    {\textit{Flutter Community}},
    \DatestampYM{2021}{01}

    \endgroup

    % \BigGap
    % \SubSection
    % {Conferences}
    % {Conferences}
    % {PDF:Conferences}

    %%%%%%%%%%%%%%%%
    %% PAGE BREAK %%
    %%%%%%%%%%%%%%%%

    \newpage

    %%%%%%%%%%%%%%%
    %% LANGUAGES %%
    %%%%%%%%%%%%%%%

    \Section
    {Languages}
    {Languages}
    {PDF:Languages}

    \BulletItem
    English: Full professional proficiency

    \BulletItem
    French: Limited working proficiency (Intermediate level from Quebec Government)

    \Gap
    \BulletItem
    Persian: Native proficiency

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %% CERTIFICATIONS AND LICENSES %%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \Section
    {Certifications \newline\&
        Licenses}
    {Certifications \& Licenses}
    {PDF:TeachingAndLicenses}

    \BulletItem
    \href{https://coursera.org/share/81c743eeff5bf3e85dfc118ab47b9407}
    {Introduction to TensorFlow for Artificial Intelligence, Machine Learning, and Deep Learning},
    \Item
    This certification course provided an in-depth understanding of Machine Learning and Deep Learning, including their applications in computer vision. Explored topics such as convolutional neural networks to enhance vision.
    Authorized by
    \href{https://deeplearning.ai}
    {\textit{DeepLearning.AI}}
    and offered through
    \href{https://coursera.org/}
    {\textit{Coursera}},
    \DatestampYM{2021}{02}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%
    %% PROFESSIONAL PROJECTS %%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%

    \Section
    {Professional\newline
        Projects}
    {Professional Projects}
    {PDF:ProfessionalProjects}

    \BulletItem
    \textbf{The Location-Based Recommendation System},
    \textit{\small{Django, Rest Framework, Scikit-learn, Flutter}}
    \hfill
    {\normalsize{
            \href{https://github.com/aliyazdi75/Resume/raw/main/BScThesis-Abstract.pdf}
            {\faFilePdf}
        }}
    \Item
    Developed a micro­service recommendation system that combines content-based and collaborative recommendation algorithms based on user location-based social media networks like Foursquare and Google Maps.
    \SubBulletItem
    Utilized \href{https://django-rest-framework.org}{Django Rest Framework} as an API service to connect the application with the server.
    \SubBulletItem
    Integrated \href{https://developer.foursquare.com}{Foursquare API} for scraping user location-based activities and \href{https://osm-internal.download.geofabrik.de}{Open Street Map} for accessing location datasets. Implemented a recommendation service for suggesting locations.
    \SubBulletItem
    Developed a Flutter application using Google Maps for the user interface.

    \BigGap
    \BulletItem
    \textbf{The Flutter Gallery Application},
    \textit{\small{Flutter}}
    \hfill
    {\normalsize{
            \href{https://medium.com/flutter-community/the-software-engineering-approach-in-cross-platform-programming-with-flutter-part-1-efcdc8a8fc26?source=friends_link&sk=ceb60f56685ce66c7f9574595748f25b}
            {\faMedium}
            \,\SubBulletSymbol\,
            \href{https://github.com/aliyazdi75/gallery/releases}
            {\faAndroid}
            \,\SubBulletSymbol\,
            \href{\CVWebpage/gallery/}
            {\faGlobe}
            \,\SubBulletSymbol\,
            \href{https://github.com/aliyazdi75/gallery}
            {\faGithub}
        }}
    \Item
    Developed a responsive Flutter gallery application for multiple platforms using a micro-service architecture. The web application is hosted on the \href{https://94.ceit.aut.ac.ir/gallery/}{Amirkabir University Website} for Alumni students.
    \SubBulletItem
    Integrated two external API providers: the University server and the Github \href{https://github.com/aliyazdi75/gallery-assets}{Repository} contents (Flutter event images).
    \SubBulletItem
    Implemented a new Flutter Navigator system and supported all navigation scenarios.

    \BigGap
    \BulletItem
    \textbf{The Flutter Chat Application},
    \textit{\small{Flutter, SignalR, WebRTC}}
    \hfill
    {\normalsize{
            \href{https://github.com/aliyazdi75/flutter_chat}
            {\faGithub}
        }}
    \Item
    Developed a full-featured Flutter chat application using SignalR and WebRTC, allowing simple text, voice, and video communication.
    \SubBulletItem
    Implemented text and video chat functionality.
    \SubBulletItem
    Established full WebRTC handshaking through SignalR, enabling offer, answer, candidate, hangup, and reject actions.
    \SubBulletItem
    Included video chat features such as switching cameras, toggling camera and microphone, and controlling the torch.

    \BigGap
    \BulletItem
    \textbf{The Flutter Portfolio Application},
    \textit{\small{Flutter}}
    \hfill
    {\normalsize{
            \href{https://snapcraft.io/aliyazdi}
            {\faLinux}
            \,\SubBulletSymbol\,
            \href{https://github.com/aliyazdi75/aliyazdi75.github.io/releases}
            {\faAndroid}
            \,\SubBulletSymbol\,
            \href{\CVWebpage}
            {\faGlobe}
            \,\SubBulletSymbol\,
            \href{https://github.com/aliyazdi75/aliyazdi75.github.io}
            {\faGithub}
        }}
    \Item
    Designed and built a responsive Flutter portfolio application that can be used on any platform.

    \BigGap
    \BulletItem
    \textbf{The Flutter Media Notification Plugin},
    \textit{\small{Java, Flutter}}
    \hfill
    {\normalsize{
            \href{https://pub.dev/packages/flutter_media_notification}
            {\faGlobe}
            \,\SubBulletSymbol\,
            \href{https://github.com/aliyazdi75/flutter_media_notification}
            {\faGithub}
        }}
    \Item
    Developed a Flutter plugin that allows developers to display media notifications and control streaming media beyond the scope of the Flutter application.

    %%%%%%%%%%%%%%%%%%%
    %% CONTRIBUTIONS %%
    %%%%%%%%%%%%%%%%%%%

    \Section
    {Contributions}
    {Contributions}
    {PDF:Contributions}

    \BulletItem
    Contributed to open-source projects by actively participating in the development process. This includes reporting issues, fixing bugs, and adding new features to the following repositories:

    \Gap
    \SubBulletItem
    \href{https://github.com/flutter/flutter/issues?q=author%3Aaliyazdi75}
    {\textbf{flutter/flutter}}

    \SubBulletItem
    \href{https://github.com/flutter/plugins/pulls?q=author%3Aaliyazdi75}
    {\textbf{flutter/plugins}}

    \SubBulletItem
    \href{https://github.com/flutter/website/pulls?q=author%3Aaliyazdi75}
    {\textbf{flutter/website}}

    %%%%%%%%%%%%%%%%%%%%%%%
    %% Academic Projects %%
    %%%%%%%%%%%%%%%%%%%%%%%

    \Section
    {Academic Projects}
    {Academic Projects}
    {PDF:AcademicProjects}

    % \begin{multicols}{2}
    % \begin{itemize}[leftmargin=*]

    \BulletItem
    \textbf{NUMEX Interpreter},
    \textit{\small{Racket}}
    \hfill
    {\normalsize{
            \href{https://github.com/aliyazdi75/NUMEX-Interpreter}
            {\faGithub}
        }}
    \Item
    Designed a simple interpreter for the NUMEX programming language using Racket as part of the Programming Languages course.

    \BigGap
    \BulletItem
    \textbf{Planet vs Zombies Game Application},
    \textit{\small{Java}}
    \hfill
    {\normalsize{
            \href{https://github.com/aliyazdi75/Planet\_vs\_Zombies}
            {\faGithub}
        }}
    \Item
    Developed a 2D game similar to Plant vs Zombies using Java and object-oriented programming concepts as part of the Advanced Computer Programming course.

    % \BigGap
    % \BulletItem
    % \textbf{Digital Watch Microcontroller},
    % \textit{\small{C}}
    % \hfill
    % {\normalsize{
    %         \href{https://github.com/aliyazdi75/Digital-Watch-with-LCD}
    %         {\faGithub}
    %     }}
    % \Item
    % Implemented a digital watch with LCD and alarm functionality using the ATMEGA16 microcontroller as part of the Microprocessor and Assembly Language course.

    % \columnbreak

    \BigGap
    \BulletItem
    \textbf{Finite State Machine Search Engine},
    \textit{\small{Java}}
    \hfill
    {\normalsize{
            \href{https://github.com/aliyazdi75/Finite-State-Machine}
            {\faGithub}
        }}
    \Item
    Designed and implemented different data structures (AVL-tree, balanced-TST, trie-tree, and hash) and performed searching operations using them as part of the Data Structures and Algorithms course.

    % \BigGap
    % \BulletItem
    % \textbf{UDP to TCP Proxy},
    % \textit{\small{Python}}
    % \hfill
    % {\normalsize{
    %         \href{https://github.com/aliyazdi75/DNS-UDP-TCP-Proxy}
    %         {\faGithub}
    %     }}
    % \Item
    % Developed a Python proxy server that receives HTTP packets over UDP and forwards them using TCP, including a DNS server, as part of the Computer Networks course.

    % \end{itemize}
    % \end{multicols}

    %%%%%%%%%%%%%%%%
    %% PAGE BREAK %%
    %%%%%%%%%%%%%%%%

    \newpage

    %%%%%%%%%%%%%%%%%%%%%%%%%
    %% TEACHING EXPERIENCE %%
    %%%%%%%%%%%%%%%%%%%%%%%%%

    \Section
    {Teaching Experience}
    {Teaching Experience}
    {PDF:TeachingExperience}

    \Entry
    \textbf{Data Structures and Algorithms},
    Amirkabir University of Technology,
    \hfill
    \textsl{\small{\DatestampYM{2017}{09}\,--\,\DatestampYM{2018}{03}}}

    \Gap
    \BulletItem
    Assisted in teaching the Data Structures and Algorithms course at Amirkabir University of Technology under the supervision of \href{https://aut.ac.ir/cv/2123/Mehdi-Dehghan-Takht-Fooladi?slc_lang=en&&cv=2123&mod=scv}
    {Prof.~Mehdi~Dehghan}
    \,\SubBulletSymbol\,
    \href{mailto:dehghan@aut.ac.ir}
    {dehghan@aut.ac.ir}
    \begin{Detail}
        \SubBulletItem
        Conducting weekly tutorial sessions to reinforce concepts and help students with problem-solving.
        \SubBulletItem
        Providing guidance and support to students during office hours and via email.
        \SubBulletItem
        Grading assignments and providing constructive feedback to students.
    \end{Detail}

    %%%%%%%%%%%%%%%%%%%%%%%%
    %% RESEARCH INTERESTS %%
    %%%%%%%%%%%%%%%%%%%%%%%%

    \Section
    {Research Interests}
    {Research Interests}
    {PDF:ResearchInterests}

    \BulletItem
    Artificial Intelligence: I am interested in various aspects of artificial intelligence, such as natural language processing, computer vision, and intelligent systems. I am excited about the potential of AI to revolutionize industries and improve decision-making processes.

    \Gap
    \BulletItem
    Machine Learning: I have a strong passion for machine learning algorithms and techniques. I enjoy exploring supervised and unsupervised learning, deep learning, and reinforcement learning. I am particularly interested in applying machine learning to solve real-world problems and extract meaningful insights from complex datasets.

    \Gap
    \BulletItem
    Software Engineering: I am intrigued by the challenges and opportunities in software engineering. I am interested in software development methodologies, software testing and quality assurance, and software architecture design. I aim to contribute to the creation of robust, scalable, and maintainable software systems.

    %%%%%%%%%%%%%%%%%%%%%%%%%
    %% RESEARCH EXPERIENCE %%
    %%%%%%%%%%%%%%%%%%%%%%%%%

    \Section
    {Research Experience}
    {Research Experience}
    {PDF:ResearchExperience}

    \Entry
    \textbf{Artificial Intelligence and Robotics Lab},
    Amirkabir University of Technology,
    \hfill
    \textsl{\small{\DatestampYM{2019}{10}\,--\,\DatestampYM{2020}{10}}}

    \Gap
    \BulletItem
    Undergraduate Research Student
    \begin{Detail}
        \SubBulletItem
        Project:
        Designing and Implementing Location Based Social Network Recommendation System
        \SubBulletItem
        Supervisor:
        \href{https://aut.ac.ir/cv/2416/Mohammad-Rahmati?slc_lang=en&&cv=2416&mod=scv}
        {Prof.~Mohammad~Rahmati}
        \,\SubBulletSymbol\,
        \href{mailto:rahmati@aut.ac.ir}
        {rahmati@aut.ac.ir}
        \SubBulletItem
        Focus: Artificial Intelligence, Software Engineering, Data Analytics
    \end{Detail}

    %%%%%%%%%%%%%%%%
    %% REFERENCES %%
    %%%%%%%%%%%%%%%%

    \Section
    {References}
    {References}
    {PDF:References}

    \BulletItem
    \href{https://linkedin.com/in/leehack}
    {\textbf{Jhinseok Lee}}
    \begin{Detail}
        \Item
        Co-organizer at GDG-Montreal,
        \href{mailto:jhin@gdgmontreal.com}
        {jhin@gdgmontreal.com}
    \end{Detail}
    \Item
    Jhin was instrumental in establishing the Flutter community in Montreal and organizing in-person events sponsored by Google to contribute to the Flutter open-source community.

    \BigGap
    \BulletItem
    \href{https://linkedin.com/in/tayormi}
    {\textbf{Ajiboye Temitope}}
    \begin{Detail}
        \Item
        Colleague at Woopen,
        \href{mailto:mrtayormi@outlook.com}
        {mrtayormi@outlook.com}
    \end{Detail}
    \Item
    I worked closely with Temi in the same team at Woopen, collaborating on maintaining and implementing new features in the mobile application.

    \BigGap
    \BulletItem
    \href{https://linkedin.com/in/srasoulzadeh}
    {\textbf{Shervin Rasoulzadeh}}
    \begin{Detail}
        \Item
        Colleague at Tarafdari,
        \href{mailto:shervin.r.1996@gmail.com}
        {shervin.r.1996@gmail.com}
    \end{Detail}
    \Item
    Shervin served as my mentor, and we collaborated in the same team at Tarafdari, working on the mobile application and the backend APIs.

    %%%%%%%%%%%%%
    %% HOBBIES %%
    %%%%%%%%%%%%%

    \Section
    {HOBBIES}
    {HOBBIES}
    {PDF:Hobbies}

    \BulletItem
    Hiking and Travelling

    \Gap
    \BulletItem
    Listening to Music and Playing a Persian Instrument called 3Tar

    \Gap
    \BulletItem
    Playing Football and Volleyball

        %%%%%%%%%%%%%
        %% CV NOTE %%
        %%%%%%%%%%%%%

        {\UseNoteFont
            \hfill
            [\textit{\CVNote}]
            \SubBulletSymbol\,
            [Clone me on
                    \href{https://github.com/aliyazdi75/Resume}
                    {\faGithub}]}

\end{Body}
\end{document}
